\Title

### 2023-07-12 cover_letter/2023-07-07_coverletter.tex
2022-10-12

Our manuscript describes a novel method inspired by neuroscience to overcome some challenges in computer vision, especially when dealing with large amounts of data, by using an event-based representation. By using heterogeneous delays at different synapses, this novel spiking neuron method is able to detect spiking motifs, and we validate the method on synthetic event-based data. Results show that this method could provide a path for future spiking neural network algorithms to consume less energy for similar performance as their analog counterparts.

>>>>

Our manuscript presents an innovative approach inspired by neuroscience to address challenges in computer vision, particularly when handling large datasets. We propose the use of an event-based representation and introduce a novel spiking neuron method that utilizes heterogeneous delays on different synapses. This method effectively detects spiking motifs, as demonstrated through experiments conducted on synthetic event-based data. Our results indicate that this approach has the potential to pave the way for future spiking neural network algorithms, offering comparable performance to their analog counterparts while consuming less energy.
